Web Service Community \\ Learning

### 2014-06-08 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\IEEEPARstart{O}{ver} 
the past years, online services have become part of many scalable business applications. The increasing reliance on online service providers has significantly influended the way web services are engineered. Web services provide a set of stateless software functions accessible at a network address over the web.

- The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interactiion, composition, and cooperation are the key challenges. Delivering high quality services considering the dynamic and unpredictable nature of the Internet is still a very critical and challenging issue.

>>>>

\IEEEPARstart{O}{ver} the past years, online services have become part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Delivering high quality services considering the dynamic and unpredictable nature of the Internet is still a very critical and challenging issue. These services can be utilized on top of intelligent decision making agents in order to maximise gain by finding ways of providing services better satisfying end users. The recent developments are shifting web services from passive and individual components to autonomouse and group-based components where interaction, composition, and cooperation are the key challenges [refrences]. To this end the idea of \emph{community} of web services by gathering services having similar functionalies but distinct non-functional properties was developed [refrences].

Web service ocmmunities faciliate the discovery of web services and also provide services with better quality. These communities act as abstract web services, communicating with external entities via same standard protocols the normal web services employ. Users send their requests to the coordinators of those communities, which play the role of their representatives or access points. The community coordinator in this \emph{community centerilized} architecture is resposible for community management tasks such as verification of credentials of new web services before accepting them to join the community and also firing web services which do not add enough value to the community.

- We want to give full distributed control to web services as autonomouse agents and distribute the task of communty management among all web services and let them decide how to maximise their efficientcy and join and create communities.
- Let agents train and learn long term expectations of each action and group they can join with
- Web services cannot find the optimal solution in big space problem of many web services
- Add rationalism and less vague decisions

%Web services provide a set of stateless software functions accessible at a network address over the web. 
%Online autonomous agent-based services are software systems providing a standard way of interoperability among different applications.

% - The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interactiion, composition, and cooperation are the key challenges.

We have implemented [OurMethodName] which
